---
title: "Errata"
subtitle: "On Coppock (2019), *Journal of Experimental Political Science* 6(1)"
format:
  pdf:
    output-file: coppock_2019b_errata.pdf
    geometry: margin=1.25in
    fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
here::i_am("errata.qmd")

results <- read_csv(here("maintained", "output", "table_2_reanalysis.csv"),
                    show_col_types = FALSE)
published <- read_csv(here("ground_truth", "published_claims.csv"),
                      col_types = cols(.default = col_character(),
                                       value_paper = col_character()))

# Every number inside a corrected sentence below is computed here, from the deposited
# data, at the time this document is rendered. That includes the numbers that were not
# wrong: a token carried over from the published sentence is inherited on trust, and
# rendering the whole sentence from the pipeline is what verifies it.
estimator_row <- function(estimator_label) {
  hit <- results[results$estimator == estimator_label, ]
  stopifnot(nrow(hit) == 1)
  hit
}

always_responder <- estimator_row("Difference-in-means among matched pairs in which both members respond")
redefined <- estimator_row("Difference-in-means")
naive <- estimator_row("Naive difference-in-means")

# One decimal place on the percentage-point scale everywhere, and the article's own
# minus sign, so a corrected sentence reads like the published one.
pts <- function(x) str_replace(sprintf("%.1f", 100 * x), "^-", "−")

# Fuller precision, for a reason line rather than a sentence.
pts3 <- function(x) str_replace(sprintf("%.3f", 100 * x), "^-", "−")

# The bounds confidence interval, which is the one quantity in Table 2 the maintained
# rewrite does not return: R 3.6.0 changed sample(), so the published pair is reproduced
# by the archive's own resampling scheme under the sampler the 2018 run used. The ground
# truth records the same thing at t2_bounds_ci_lower and t2_bounds_ci_upper, where the
# defect locus is `environment` rather than anything the paper did.
bootstrap <- read_csv(here("maintained", "output", "text_bootstrap_sampler.csv"),
                      show_col_types = FALSE)
archive_boot <- bootstrap[bootstrap$method == "Archive resampling scheme, pre-3.6 sampler", ]
stopifnot(nrow(archive_boot) == 1)

# A Table 2 cell on the article's own scale: three decimal places, which is what every
# other limit in the 95% CI column is given to, and the article's own minus sign.
cell <- function(x) str_replace(sprintf("%.3f", x), "^-", "−")

# The article's own Table 2 cell, quoted from the extraction of the published page
# rather than retyped here.
table2 <- function(claim_id) {
  value <- published$value_paper[published$claim_id == claim_id]
  stopifnot(length(value) == 1)
  str_replace(value, "^-", "−")
}
```

```{r entries}
# THE ERRATA SPINE. Every entry is defined once, here, and rendered from this tibble into
# this document and into the machine-readable errata_entries.csv written at the bottom of
# the file, which is what any other document carrying these corrections reads. Before the
# spine existed an entry was written out in prose wherever it was needed, and the copies
# had already diverged.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here. Nothing else in a field is markup, so the same string can be set by any of them.
#
# Numbering is the published note's and is APPEND-ONLY: entry 1 can already have been cited,
# so a later finding is added at the end and never interleaved.
#
# A published or corrected value that the pipeline computes stays computed: the field is
# built with str_glue() so the number is produced when this document renders, not typed.
#
# claim_ids is the semicolon-separated list of ground-truth claim_id values the entry
# corrects, and it is what makes "is this finding published?" a query rather than a reading
# of every note. It is empty where an entry has no ground-truth row, which is normal for a
# bibliographic or structural entry. ground_truth/build_ground_truth.R refuses to build if
# any id here is absent from the ground truth.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note, ~claim_ids,

  1, "quantity", "pipeline", "full",
  "The Always-Responder estimate disagrees with Table 2",
  "published p. 3",
  "Under the unverifiable assumption that both pair members would also have responded if the treatment assignment had been switched, I estimate the ATE among this subgroup to be [[−5.5]] points (SE = 2.5 points).",
  str_glue("Under the unverifiable assumption that both pair members would also have responded if the treatment assignment had been switched, I estimate the ATE among this subgroup to be [[{pts(always_responder$estimate)}]] points (SE = {pts(always_responder$std_error)} points)."),
  str_glue(
    "Table 2 prints {table2('t2_ar_estimate')} for the same estimate, which is ",
    "{pts(always_responder$estimate)} points. The estimate is ",
    "{pts3(always_responder$estimate)} points, so the table rounds and the sentence ",
    "truncates, and the article disagrees with itself about the number a reader would quote. ",
    "The standard error is {pts3(always_responder$std_error)} points and is correct as ",
    "published."),
  "p3_ar_ate_points",

  2, "quantity", "pipeline", "full",
  "The standard error on the redefined outcome",
  "published p. 3",
  "Finally, using the redefined outcome, I estimate the ATE to be a [[6]] point decrease in friendliness (SE = [[1.7]] points).",
  str_glue("Finally, using the redefined outcome, I estimate the ATE to be a [[{str_remove(pts(redefined$estimate), '−')}]] point decrease in friendliness (SE = [[{pts(redefined$std_error)}]] points)."),
  str_glue(
    "Table 2 prints no standard errors, so this figure appears in the article only here. The ",
    "standard error is {pts3(redefined$std_error)} points, which rounds to ",
    "{pts(redefined$std_error)}; the sentence truncates it, as the sentence before it does. ",
    "The point estimate is a decrease of {str_remove(pts3(redefined$estimate), '−')} points, ",
    "which the sentence truncates to a whole number in the same way; it is given here at ",
    "the decimal the corrected standard error is given to."),
  "p3_redefined_se_points",

  3, "wording", "remaster", "brief",
  "The naive estimate is printed without its unit",
  "published p. 3",
  "(−3.5 [[percentage]], SE = 2.0 points)",
  str_glue("({pts(naive$estimate)} [[percentage points]], SE = {pts(naive$std_error)} points)"),
  str_glue(
    "Found while preparing the remastered edition. Every other quantity in the sentence ",
    "and in the one before it is given in points, and Table 2 prints ",
    "{table2('t2_naive_estimate')} for this estimate, which is {pts(naive$estimate)} ",
    "percentage points. The missing word is the one the rest of the paragraph uses, so ",
    "it is supplied rather than guessed at, and the figure itself is correct as published."),
  "",

  4, "float", "remaster", "brief",
  "Table 2's bounds interval drops a digit the rest of its column carries",
  "published p. 3, Table 2",
  str_glue("[[Table 2's bounds row, whose 95% confidence interval opens at ",
           "{table2('t2_bounds_ci_lower')}]]"),
  str_glue("[[{cell(archive_boot$conf_low)}, the same value at the three decimal places ",
           "the rest of the column is given to]]"),
  str_glue(
    "Found while preparing the remastered edition. The value is not in dispute and no ",
    "estimate moves: the limit is {cell(archive_boot$conf_low)}, and the five other ",
    "limits in the same column are printed to three places ",
    "({table2('t2_naive_ci_lower')}, {table2('t2_naive_ci_upper')}, ",
    "{table2('t2_redefined_ci_lower')}, {table2('t2_redefined_ci_upper')} and ",
    "{table2('t2_bounds_ci_upper')}). Line 187 of the deposited ",
    "`aec_replication_JEPS.R` builds the cell as ",
    "`paste0(\"[\", round(ci_lower, 3), \", \", round(ci_upper, 3), \"]\")`, and ",
    "`round()` returns a numeric that `paste0` converts with `as.character`, which drops ",
    "a trailing zero; the other limits keep their three places only because none of them ",
    "ends in one. This is the one cell of Table 2 the maintained rewrite does not return: ",
    "R 3.6.0 changed `sample()`, so it is reproduced under the archive's own resampling ",
    "scheme and the sampler the 2018 run used, which is what ",
    "`maintained/output/text_bootstrap_sampler.csv` records."),
  "t2_bounds_ci_lower"
) |>
  mutate(across(c(title, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# Every id an entry claims to correct must be a real ground-truth claim. The build gate in
# ground_truth/build_ground_truth.R checks the same property from the other side; checking it
# here too means a dangling id cannot survive a render.
gt_ids <- read_csv(here("ground_truth", "coppock_2019b_ground_truth.csv"),
                   show_col_types = FALSE)$claim_id
cited_ids <- entries$claim_ids |>
  str_split(";") |>
  unlist() |>
  str_trim() |>
  discard(\(x) is.na(x) | x == "")
stopifnot(all(cited_ids %in% gt_ids))

# The prose below counts the entries in words, as the note has always done.
n_entries_word <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
                    "ten", "eleven", "twelve")[nrow(entries)]

# The spine's markup, resolved for this document.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
```

This note lists `r n_entries_word` corrections to "Avoiding Post-Treatment Bias in Audit Experiments," published in the *Journal of Experimental Political Science* 6(1), 1-4, doi [10.1017/XPS.2018.9](https://doi.org/10.1017/XPS.2018.9). Three are in the reanalysis paragraph on page 3 and the fourth is in Table 2, and **none of them changes a conclusion of the paper.** Two are misstated numbers, in each case the correct value truncated rather than rounded at the last digit the sentence prints; the third is an estimate printed without its unit; the fourth is a table cell printed to one fewer decimal place than the column it sits in, with the value itself unchanged. Every estimate Table 2 reports is right, and the argument the note makes about post-treatment conditioning is unaffected.

Every number in a corrected sentence below is computed from the deposited replication archive ([10.7910/DVN/6NVI9C](https://doi.org/10.7910/DVN/6NVI9C)) at the time this document is rendered, including the numbers that were not wrong. The code and output supporting each correction are at [github.com/active-maintenance-aec/coppock_2019b](https://github.com/active-maintenance-aec/coppock_2019b).

**Every quantity on the percentage-point scale is stated to one decimal place, and bold marks the corrections.** Where the article gives a figure in whole points and the corrected sentence gives it to one decimal, that is marked like any other change: a corrected sentence below differs from the published one only where it is bold. Where a fuller value matters it is given in the note beneath the entry.

```{r render-entries, results="asis"}
# A heading is only a heading when a blank line precedes it, so every emitted entry opens
# with one.
walk(seq_len(nrow(entries)), function(i) {
  e <- entries[i, ]
  cat("\n\n## ", e$entry, ". ", e$title, "\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", bold(e$corrected), "\n\n", e$note, "\n", sep = "")
})
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered. Anything else that
# carries these corrections reads it rather than keeping its own copy, so the two cannot drift.
write_csv(entries, here("errata_entries.csv"))
```
